Cultural Evolution of Conservation Behavior at the Intersection of Working

### 2020-09-30 DissertationProposal/DissertationProposal.Rmd
Figures, equations, and plots. Mostly equations

```{r abmOutput, echo=FALSE, fig.cap="Fifteen example runs of the current, single-group agent based model", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/ABM_Output.png")
```

## Expected Products
I plan to communicate the findings of this project both to the academic community and to non-scientists. The insights gained from this model will be published in a peer reviewed, academic journal such as Environmental Modeling and Software. This paper will show logically how we expect that protected areas function in the context of community level cooperative conservation. An example of how this model may inform implementation of protected areas for various resource mobilities or starting resource degradation is displayed in figure (XXX).

@@

# Chapter 2: Effects of inter-group resource competition and selection on community adoption of costly conservation policy.

@@

@@

```{r csp2, echo=FALSE, fig.cap="Simulated outputs showing a possible relationship between stove copying fidelity and geographic distance between the demonstrator and copier", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/CSP2.png")
```
# Conclusion

>>>>

```{r abmOutput, echo=FALSE, fig.cap="Fifteen example runs of the current, single group agent-based model", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/ABM_Output.png")
```

## Expected Products
I plan to communicate the findings of this project both to the academic community and to non-scientists. The insights gained from this model will be published in a peer reviewed, academic journal such as Environmental Modeling and Software. This paper will show logically how we expect that protected areas function in the context of community level cooperative conservation. An example of how this model may inform implementation of protected areas for various resource mobilities or starting resource degradation is displayed in figures \@ref(fig:abmSim1) & \@ref(fig:abmSim2).

@@

```{r abmSim1, echo=FALSE, fig.cap="Simulated agent-based model output of conservation adoption under single group dynamics.", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmSim1.png")
```

```{r abmSim2, echo=FALSE, fig.cap="Simulated agent-based model output of conservation adoption under multiple group dynamics.", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch1/abmSim2.png")
```
# Chapter 2: Effects of inter-group resource competition and selection on community adoption of costly conservation policy.

@@

Inline LaTeX equations can be written in a pair of dollar signs using the LaTeX syntax, e.g., $f(k) = {n \choose k} p^{k} (1-p)^{n-k}$  math expressions of the display style can be written in a pair of double dollar signs, e.g.,

$$f(k) = {n \choose k} p^{k} (1-p)^{n-k}$$, and the output looks like this:

Cultural fst equation

$$F_{STx} = \frac{\frac{n_{i}}{n_{i}+n_{j}} (p_{i}-\bar{p})^2 + \frac{n_{j}}{n_{i}+n_{j}} (p_{j}-\bar{p})^2}{\bar{p}(1-\bar{p})}$$

Rogers inequality
$$\frac{c_{w}}{b_{p}} < \frac{F_{ST}}{(1-F_{ST})}$$

Price equation
$$ \bar{W} \Delta \bar{Z} = \text{cov}(W_{g},Z_{g}) + E[\text{cov}(W_{ig},Z_{ig})]$$

@@

```{r csp2, echo=FALSE, fig.cap="Simulated outputs showing a possible relationship between stove copying fidelity and geographic distance between the demonstrator and copier", out.width = "100%", fig.align='center', dpi=72, fig.pos= "H"}
knitr::include_graphics("Figures/Ch3/CSP2.png")
```
# Conclusion
[@dudley2018essential]
